---
output:
  html_document:
    fig_width: 1
---

<style type="text/css">
.nav.navbar-nav.navbar-right a {
    color: white;
}
.navbar {
  background-color:maroon;
  border-color:black;
  icon-color:white;
}
.navbar-brand {
color:black!important;
}
body{ /* Normal  */
      font-size: 15px;
  }
h1.title {
  font-size: 32px;
}
h3 { /* Header 3 */
  font-size: 24px;
  color: DarkRed;
}
</style>

<style>
.column-f1{
  float: left;
  width: 20%;
  text-align: left;
}
.column-f2{
  float: right;
  width: 20%;
  text-align: right;
}

.column-left{
  float: left;
  width: 45%;
  text-align: left;
}
.column-right{
  float: right;
  width: 45%;
  text-align: left;
}
.column{
  float: left;
  width: 100%;
  text-align: left;
} 
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(reshape2)
library(ggplot2)
# library(printr)
library(knitr)
```

## Notas

----

<div class="column-left">

|     RA|    P1| Faltas|
|:------|:----:|------:|
| 119228|  8,75|      0|
| 138347|  9,50|      3|
| 147114|  5,75|      2|
| 154954|  8,50|      3|
| 155766|  1,50|      4|
| 157276|  F   |      4|
| 158365|  2,75|      1|
| 165150|  5,25|      1|
| 168614| 10,00|      2|
| 170789|  6,50|      0|
| 170882|  5,00|      3|
| 171889|  5,25|      5|
| 173019|  F   |      4|
| 174763|  3,50|      0|

</div>
<div class="column-right">

|     RA|    P1| Faltas|
|:------|:----:|------:|
| 175238|  2,25|      7|
| 175247|  5,25|      4|
| 175615|  7,25|      0|
| 175913|  4,25|      0|
| 177349|  8,75|      1|
| 181987|  2,25|      0|
| 183800|  4,50|      1|
| 183848|  5,25|      3|
| 183883|  6,25|      2|
| 184050|  3,25|      0|
| 184679|  6,00|      1|
| 185451|  6,25|      0|
| 186109|  7,00|      0|
| 194478|  6,25|      0|

</div>

<div class="column">
----

### Resumo das Notas 

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**P1** | 1,50|    4,31|   5,5| 5,65|    6,88| 10,00|



```{r, echo=FALSE, include=FALSE, warning=FALSE}
library("gdata")
notas = read.xls("/Users/Larissa/Desktop/1S2019/ME_951/Provas/Notas.xls",header = TRUE)
require(xtable)
kable(notas)
notasp1<-notas$P1
notasp1[notasp1==0]<-NA
b<-rbind(summary(notasp1))
```

```{r, echo=FALSE, fig.width=10, fig.height=5, warning=FALSE}
par(mfrow=c(1,1))
# boxplot(notasp1,col="lightblue", type=3, ylim=c(0,10),main="P1")
# points(mean(notasp1,na.rm=TRUE))
# abline(h=6,lty=2)
boxplot(notasp1, horizontal=TRUE,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10))
points(mean(notasp1,na.rm=TRUE))
abline(v=6,lty=2)

```

### Resumo das Notas P1/Faltas

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**Faltas<=3** | 2,25|    4,62|   6,13| 6,03|    7,19| 10,00|
**Faltas>=4** | 1,50|    2,06|   3,75| 3,57|    5,25| 5,25|

<center>
```{r, echo=FALSE, fig.width=7, fig.height=5, warning=FALSE}
par(mfrow=c(1,1))
faltas<-notas$Faltas
faltas[faltas==0]<-faltas[faltas==1]<-faltas[faltas==2]<-faltas[faltas==3]<-"Faltas<=3"
faltas[faltas==4]<-faltas[faltas==5]<-faltas[faltas==7]<-"Faltas>=4"
faltas<-as.factor(faltas)
boxplot(notasp1~faltas,col="rosybrown3", type=3, ylim=c(0,10))
#abline(v=6,lty=2)
#tapply(notasp1,faltas,summary)
#boxplot(notasp1~as.factor(notas$Faltas),col="rosybrown3", type=3, ylim=c(0,10))
```
</center>

</div>

