---
output:
  html_document:
    fig_width: 1
---

<style type="text/css">
.nav.navbar-nav.navbar-right a {
    color: white;
}
.navbar {
  background-color:maroon;
  border-color:black;
  icon-color:white;
}
.navbar-brand {
color:black!important;
}
body{ /* Normal  */
      font-size: 15px;
  }
h1.title {
  font-size: 32px;
}
h3 { /* Header 3 */
  font-size: 24px;
  color: DarkRed;
}
</style>

<style>
.column-f1{
  float: left;
  width: 20%;
  text-align: left;
}
.column-f2{
  float: right;
  width: 20%;
  text-align: right;
}

.column-left{
  float: left;
  width: 45%;
  text-align: left;
}
.column-right{
  float: right;
  width: 45%;
  text-align: left;
}
.column{
  float: left;
  width: 100%;
  text-align: left;
} 
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(reshape2)
library(ggplot2)
# library(printr)
library(knitr)
```

## Notas

----

|     RA|    P1|    P2|   P3| Faltas|   MF|S         |
|------:|-----:|-----:|----:|------:|----:|:---------|
| 119228|  8,75| 10,00| 9,75|      0| 9,53|<span style="color:green"> APROVADO </span>  |
| 138347|  9,50|  8,50| 0,00|      7| 5,40|<span style="color:green"> APROVADO </span>  |
| 147114|  5,75|  4,75| 2,50|      4| 4,15|<span style="color:maroon"> EXAME </span>     |
| 154954|  8,50|  8,00| 8,50|      4| 8,35|<span style="color:green"> APROVADO </span>  |
| 155766|  1,50|  0,00| 0,00|     15| 0,45|<span style="color:red"> REPROVADO FALTA/NOTA </span> |
| 157276|  4,25|  3,75| 1,00|      7| 2,80|<span style="color:maroon"> EXAME </span>     |
| 158365|  2,75|  7,75| 6,00|      4| 5,55|<span style="color:green"> APROVADO </span>  |
| 165150|  5,25|  0,75| 2,25|      3| 2,70|<span style="color:maroon"> EXAME </span>     |
| 168614| 10,00|  5,75| 6,75|      4| 7,43|<span style="color:green"> APROVADO </span>  |
| 170789|  6,50| 10,00| 6,50|      1| 7,55|<span style="color:green"> APROVADO </span>  |
| 170882|  5,00|  2,75| 1,50|      4| 2,93|<span style="color:maroon"> EXAME </span>     |
| 171889|  5,25|  5,25| 2,00|      6| 3,95|<span style="color:maroon"> EXAME </span>     |
| 173019|  0,00|  0,00| 0,00|     14| 0,00|<span style="color:red"> REPROVADO FALTA/NOTA </span> |
| 174763|  3,50|  4,75| 4,50|      2| 4,28|<span style="color:maroon"> EXAME </span>     |
| 175238|  2,25|  2,50| 4,50|      7| 3,23|<span style="color:maroon"> EXAME </span>     |
| 175247|  5,25|  5,25| 6,00|      5| 5,55|<span style="color:green"> APROVADO </span>  |
| 175615|  7,25|  8,75| 6,50|      1| 7,40|<span style="color:green"> APROVADO </span>  |
| 175913|  4,25|  1,75| 5,75|      4| 4,10|<span style="color:maroon"> EXAME </span>     |
| 177349|  8,75|  8,00| 3,25|      7| 6,33|<span style="color:green"> APROVADO </span>  |
| 183800|  4,50|  5,25| 5,50|      4| 5,13|<span style="color:green"> APROVADO </span>  |
| 183848|  5,25|  5,75| 3,00|      6| 4,50|<span style="color:maroon"> EXAME </span>     |
| 183883|  6,25|  7,25| 3,75|      3| 5,55|<span style="color:green"> APROVADO </span>  |
| 184050|  3,25|  3,50| 7,50|      3| 5,03|<span style="color:green"> APROVADO </span>  |
| 184679|  6,00|  1,50| 3,50|      2| 3,65|<span style="color:maroon"> EXAME </span>     |
| 185451|  6,25|  2,75| 7,50|      2| 5,70|<span style="color:green"> APROVADO </span>  |
| 186109|  7,00|  6,75| 6,50|      2| 6,73|<span style="color:green"> APROVADO </span>  |
| 194478|  6,25|  8,50| 7,00|      1| 7,23|<span style="color:green"> APROVADO </span>  |

----

### Resumo das Notas 

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**P1** | 0,00|    4,25|   5,25| 5,52|    6,75| 10,00|
**P2** | 0,00|    2,75|   5,25| 5,17|    7,87| 10,00|
**P3** | 0,00|    2,37|   4,50| 4,50|    6,50| 9,75|
**MF** | 0,00|    3,80|   5,13| 5,01|    6,53| 9,53|

\ | APROVADOS | EXAME | REPROVADOS FALTA/NOTA |
:-:|:---------:|:------:|:------:|
Frequência | 15 | 10 | 2 |

```{r, echo=FALSE, include=FALSE, warning=FALSE}
library("gdata")
notas = read.xls("/Users/Larissa/Desktop/1S2019/ME_951/Provas/Notas.xls",header = TRUE)
notas = read.table("/Users/Larissa/Desktop/1S2019/ME_951/Provas/notas.txt",header = TRUE)
require(xtable)
kable(notas[,c(1,2,3,4,7,8,9)])
notasp1<-notas$P1
b<-rbind(summary(notasp1))
notasp2<-notas$P2
b1<-rbind(summary(notasp2))
notasp3<-notas$P3
b2<-rbind(summary(notasp3))
notasmf<-notas$MF
b3<-rbind(summary(notasmf))
```

```{r, echo=FALSE, fig.width=10, fig.height=5, warning=FALSE}
par(mfrow=c(1,4))
# boxplot(notasp1,col="lightblue", type=3, ylim=c(0,10),main="P1")
# points(mean(notasp1,na.rm=TRUE))
# abline(h=6,lty=2)
boxplot(notasp1, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="P1",cex.main=1)
points(mean(notasp1,na.rm=TRUE))
abline(h=6,lty=2)
boxplot(notasp2, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="P2",cex.main=1)
points(mean(notasp2,na.rm=TRUE))
abline(h=6,lty=2)
boxplot(notasp3, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="P3",cex.main=1)
points(mean(notasp3,na.rm=TRUE))
abline(h=6,lty=2)
boxplot(notasmf, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="MF",cex.main=1)
points(mean(notasmf,na.rm=TRUE))
abline(h=5,lty=2)
```

<!-- ### Resumo das Notas P1/Faltas -->

<!-- \    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.| -->
<!-- :----:|:----:|:-------:|:------:|:----:|:-------:|:----:| -->
<!-- **Faltas<=3** | 2,75|    5,00|   6,25| 6,21|    7,25| 10,00| -->
<!-- **Faltas>=4** | 0,00|    1,50|   2,25| 2,85|    5,25| 5,25| -->

<!-- <center> -->
<!-- ```{r, echo=FALSE, fig.width=7, fig.height=5, warning=FALSE} -->
<!-- par(mfrow=c(1,1)) -->
<!-- faltas<-notas$FaltasP1 -->
<!-- faltas[faltas==0]<-faltas[faltas==1]<-faltas[faltas==2]<-faltas[faltas==3]<-"Faltas<=3" -->
<!-- faltas[faltas==4]<-faltas[faltas==5]<-faltas[faltas==7]<-"Faltas>=4" -->
<!-- faltas<-as.factor(faltas) -->
<!-- boxplot(notasp1~faltas,col="rosybrown3", type=3, ylim=c(0,10)) -->
<!-- #abline(v=6,lty=2) -->
<!-- #tapply(notasp1,faltas,summary) -->
<!-- #boxplot(notasp1~as.factor(notas$Faltas),col="rosybrown3", type=3, ylim=c(0,10)) -->
<!-- ``` -->
<!-- </center> -->

<!-- ### Resumo das Notas P2/Faltas -->

<!-- \    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.| -->
<!-- :----:|:----:|:-------:|:------:|:----:|:-------:|:----:| -->
<!-- **Faltas<5** | 0,75|    3,50|   5,50| 5,63|    7,75| 10,00| -->
<!-- **Faltas>=5** | 0,00|    0,62|   3,12| 2,75|    4,69| 5,25| -->

<!-- <center> -->
<!-- ```{r, echo=FALSE, fig.width=7, fig.height=5, warning=FALSE} -->
<!-- par(mfrow=c(1,1)) -->
<!-- faltas<-notas$Faltas -->
<!-- faltas[faltas<5]<-1 -->
<!-- faltas[faltas>=5]<-2 -->
<!-- faltas[faltas==1]<-"Faltas<5" -->
<!-- faltas[faltas==2]<-"Faltas>=5" -->
<!-- faltas<-as.factor(faltas) -->
<!-- boxplot(notasp2~faltas,col="rosybrown3", type=3, ylim=c(0,10)) -->
<!-- #abline(v=6,lty=2) -->
<!-- #tapply(notasp2,faltas,summary) -->
<!-- #boxplot(notasp2~as.factor(notas$Faltas),col="rosybrown3", type=3, ylim=c(0,10)) -->
<!-- ``` -->

</center>


