---
output:
  html_document:
    fig_width: 1
---

<style type="text/css">
.nav.navbar-nav.navbar-right a {
    color: white;
}
.navbar {
  background-color:maroon;
  border-color:black;
  icon-color:white;
}
.navbar-brand {
color:black!important;
}
body{ /* Normal  */
      font-size: 15px;
  }
h1.title {
  font-size: 32px;
}
h3 { /* Header 3 */
  font-size: 24px;
  color: DarkRed;
}
</style>

<style>
.column-f1{
  float: left;
  width: 20%;
  text-align: left;
}
.column-f2{
  float: right;
  width: 20%;
  text-align: right;
}

.column-left{
  float: left;
  width: 47%;
  text-align: left;
}
.column-right{
  float: right;
  width: 47%;
  text-align: left;
}
.column{
  float: left;
  width: 100%;
  text-align: left;
} 
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(reshape2)
library(ggplot2)
# library(printr)
library(knitr)
library(plotly)
library(DT)

```

## Notas

----

```{r, echo=FALSE, include=FALSE, warning=FALSE}
library("gdata")
notas = read.table("/Users/Larissa/Desktop/2S2019/ME414/Provas/notas.txt",header = TRUE)
require(xtable)
kable(notas[,c(1,2,8)])
notasp1<-notas$Prova1
b<-rbind(summary(notasp1))
```

```{r, echo=FALSE, warning=FALSE}
library("gdata")
notas = read.table("/Users/Larissa/Desktop/2S2019/ME414/Provas/notas.txt",header = TRUE)
require(xtable)
#kable(notas[,c(1,2,8)])
dd <- data.frame(v1=notas[,1], v2=notas[,2], v3=notas[,8], v4=rep(0,63))
colnames(dd)=c("RA", "P1", "Faltas"," ")
dd[dd[,3]>=8,4] <- '<span style="color:maroon"> REPROVADO POR FALTA </span>'
dd[dd[,3]<=7,4] <- " "
notasp1<-notas$Prova1
b<-rbind(summary(notasp1))
datatable(dd, rownames=FALSE, escape = FALSE, options = list(columnDefs = list(list(className = 'dt-right', targets = 3))))
```

----

</br>

### Resumo das Notas 

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**P1** | 0,00|    6,00|   6,70| 6,55|    8,00| 10,00|

<center>
```{r, echo=FALSE, fig.width=6, fig.height=5, warning=FALSE}
par(mfrow=c(1,1))
# boxplot(notasp1,col="lightblue", type=3, ylim=c(0,10),main="P1")
# points(mean(notasp1,na.rm=TRUE))
# abline(h=6,lty=2)
boxplot(notasp1, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="P1",cex.main=1)
points(mean(notasp1,na.rm=TRUE),pch=8)
abline(h=6,lty=2)
```
</center>

### Resumo das Notas P1/Faltas

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**Faltas<=3** | 4,00|    6,00|   7,3| 7,00|    8,20| 10,00|
**Faltas>=4** | 0,00|    0,00|   6,00| 4,30|    7,00| 8,70|

<center>
```{r, echo=FALSE, fig.width=6, fig.height=5, warning=FALSE}
par(mfrow=c(1,1))
faltas<-notas$FaltasP1
faltas[faltas==0]<-faltas[faltas==1]<-faltas[faltas==2]<-faltas[faltas==3]<-"Faltas<=3"
faltas[faltas==4]<-faltas[faltas==5]<-faltas[faltas==6]<-faltas[faltas==7]<-faltas[faltas==8]<-faltas[faltas==11]<-faltas[faltas==12]<-"Faltas>=4"
faltas<-as.factor(faltas)
boxplot(notasp1~faltas,col="rosybrown3", type=3, ylim=c(0,10))
#abline(v=6,lty=2)
#tapply(notasp1,faltas,summary)
#boxplot(notasp1~as.factor(notas$Faltas),col="rosybrown3", type=3, ylim=c(0,10))
```
</center>

<!-- ### Resumo das Notas P2/Faltas -->

<!-- \    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.| -->
<!-- :----:|:----:|:-------:|:------:|:----:|:-------:|:----:| -->
<!-- **Faltas<5** | 0,75|    3,50|   5,50| 5,63|    7,75| 10,00| -->
<!-- **Faltas>=5** | 0,00|    0,62|   3,12| 2,75|    4,69| 5,25| -->

<!-- <center> -->
<!-- ```{r, echo=FALSE, fig.width=7, fig.height=5, warning=FALSE} -->
<!-- par(mfrow=c(1,1)) -->
<!-- faltas<-notas$Faltas -->
<!-- faltas[faltas<5]<-1 -->
<!-- faltas[faltas>=5]<-2 -->
<!-- faltas[faltas==1]<-"Faltas<5" -->
<!-- faltas[faltas==2]<-"Faltas>=5" -->
<!-- faltas<-as.factor(faltas) -->
<!-- boxplot(notasp2~faltas,col="rosybrown3", type=3, ylim=c(0,10)) -->
<!-- #abline(v=6,lty=2) -->
<!-- #tapply(notasp2,faltas,summary) -->
<!-- #boxplot(notasp2~as.factor(notas$Faltas),col="rosybrown3", type=3, ylim=c(0,10)) -->
<!-- ``` -->
<!-- </center> -->


