---
output:
  html_document:
    fig_width: 1
---

<style type="text/css">
.nav.navbar-nav.navbar-right a {
    color: white;
}
.navbar {
  background-color:maroon;
  border-color:black;
  icon-color:white;
}
.navbar-brand {
color:black!important;
}
body{ /* Normal  */
      font-size: 15px;
  }
h1.title {
  font-size: 32px;
}
h3 { /* Header 3 */
  font-size: 24px;
  color: DarkRed;
}
</style>

<style>
.column-f1{
  float: left;
  width: 20%;
  text-align: left;
}
.column-f2{
  float: right;
  width: 20%;
  text-align: right;
}

.column-left{
  float: left;
  width: 47%;
  text-align: left;
}
.column-right{
  float: right;
  width: 47%;
  text-align: left;
}
.column{
  float: left;
  width: 100%;
  text-align: left;
} 
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(reshape2)
library(ggplot2)
# library(printr)
library(knitr)
library(plotly)
library(DT)

```

## Notas

----

```{r, echo=FALSE, include=FALSE, warning=FALSE}
library("gdata")
notas = read.table("/Users/Larissa/Desktop/2S2019/ME414/Provas/notas.txt",header = TRUE)
require(xtable)
kable(notas[,c(1,2,3,5,8)])
notasp1<-notas$Prova1
notasp2<-notas$Prova2
b1<-rbind(summary(notasp1))
b2<-rbind(summary(notasp2))
```

```{r, echo=FALSE, warning=FALSE}
library("gdata")
notas = read.table("/Users/Larissa/Desktop/2S2019/ME414/Provas/notas.txt",header = TRUE)
require(xtable)
dd <- data.frame(v1=notas[,1], v2=notas[,2], v3=notas[,3], v4=notas[,5], v5=notas[,8], v6=rep(0,58))
colnames(dd)=c("RA", "P1", "P2", "MF",  "Faltas"," ")
dd[dd[,5]>=8,6] <- '<span style="color:maroon"> REPROVADO POR FALTA </span>'
dd[dd[,5]<=7,6] <- " "
datatable(dd, rownames=FALSE, escape = FALSE, options = list(columnDefs = list(list(className = 'dt-right', targets = 3))))
```

----

</br>

### Resumo das Notas 

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**P1** | 0,00|    6,00|   6,70| 6,55|    8,00| 10,00|
**P2** | 0,00|    3,00|   5,00| 5,20|    7,37| 10,00|


<center>
```{r, echo=FALSE, fig.width=8, fig.height=5, warning=FALSE}
par(mfrow=c(1,2))
boxplot(notasp1, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="P1",cex.main=1)
points(mean(notasp1,na.rm=TRUE),pch=8)
abline(h=6,lty=2)
boxplot(notasp2, horizontal=F,  outline=TRUE,col="rosybrown3", type=3, ylim=c(0,10),main="P2",cex.main=1)
points(mean(notasp2,na.rm=TRUE),pch=8)
abline(h=6,lty=2)
```
</center>

### Resumo das Notas P2/Faltas

\    | Min.| 1st Qu.| Median| Mean| 3rd Qu.| Max.|
:----:|:----:|:-------:|:------:|:----:|:-------:|:----:|
**Faltas<=5** | 0,00|    4,00|   6,00| 5,72|    7,87| 10,00|
**Faltas>5**  | 0,00|    0,00|   0,00| 1,87|    2,75| 8,00|

<center>
```{r, echo=FALSE, fig.width=6, fig.height=5, warning=FALSE}
par(mfrow=c(1,1))
faltas<- ifelse(notas$Faltas<=5,"Faltas<=5","Faltas>5")
faltas<-as.factor(faltas)
boxplot(notasp2~faltas,col="rosybrown3", type=3, ylim=c(0,10))
#tapply(notasp2,faltas,summary) 
```
</center>


